Code example

### 2021-05-06 03_R_Scripts/code_example.Rmd
:truck: :bathtub: Clean and rename files

```{r download_data_dummy, eval = FALSE}
precipitation <- raster::getData(name = "worldclim", lon = 3, lat = 38,
                                 res = 0.5, var = "prec", path = "R/")
```

@@

```{r base_plot, eval = FALSE}
# pdf(file = "R/Figures/base_plot.pdf")

@@

# ggplot2::ggsave(filename = "R/Figures/ggplot2.pdf")
```

@@

# tmap::tmap_save(plot_tm, "R/Figures/tmap.pdf")
```

>>>>

```{r download_data_dummy, eval = FALSE}
precipitation <- raster::getData(name = "worldclim", lon = 3, lat = 38,
                                 res = 0.5, var = "prec", path = "03_R_Scripts/")
```

@@

```{r base_plot, eval = FALSE}
# pdf(file = "03_R_Scripts/Figures/base_plot.pdf")

@@

# ggplot2::ggsave(filename = "03_R_Scripts/Figures/ggplot2.pdf")
```

@@

# tmap::tmap_save(plot_tm, "03_R_Scripts/Figures/tmap.pdf")
```
